Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/intro.tex
Some small tweaks to the intro and model sections.

Borrowing from the intuition of stochastic blockmodels, we propose a novel continuous-time model of network-based event sequences where latent clusters of nodes share similar patterns of interaction.
Our approach employs a flexible framework for  specifying how the process depends on the previous history of events \cite{AalenOddO.2008, Butts2008}.
In this way one can compare theories about the underlying processes and make predictions about future data conditioned on the past.
{\color{red} ...and simultaneously adjust for heterogeneity in these
  processes?}

>>>>

Borrowing from the intuition of stochastic blockmodels, we propose a novel continuous-time model family for network-based event sequences where latent clusters of nodes share similar patterns of interaction.
Our approach employs a flexible framework for  specifying how the process depends on the previous history of events \cite{AalenOddO.2008, Butts2008}.
In this way one can compare theories about underlying processes and make predictions about future data conditioned on the past, simultaneously adjusting for unobserved heterogeneity.
